\documentclass{article}
\usepackage{hyperref}

\title{Troubleshooting Guide for ADAM}
\author{AOx0}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document provides troubleshooting instructions for the ADAM project. It includes sections on common issues and their solutions.

\section{Common Issues}
\subsection{Issue 1: Build Failure}
\textbf{Description:} The build process fails with an error message.

\textbf{Solution:}
\begin{enumerate}
    \item Ensure all dependencies are installed as mentioned in the prerequisites section of the usage guide.
    \item Check the error message for specific details and address the issue accordingly.
    \item Clean the build directory and try building again:
    \begin{verbatim}
    cargo clean
    cargo build
    \end{verbatim}
\end{enumerate}

\subsection{Issue 2: Runtime Error}
\textbf{Description:} The application crashes or behaves unexpectedly during runtime.

\textbf{Solution:}
\begin{enumerate}
    \item Check the log files for error messages and stack traces.
    \item Ensure all environment variables are set correctly.
    \item Verify that the correct version of dependencies is installed.
    \item Run the application in debug mode to get more detailed error messages:
    \begin{verbatim}
    cargo run
    \end{verbatim}
\end{enumerate}

\subsection{Issue 3: Network Connectivity Problems}
\textbf{Description:} The application is unable to connect to the network or other services.

\textbf{Solution:}
\begin{enumerate}
    \item Check the network configuration and ensure the network interface is up and running.
    \item Verify that the firewall settings are not blocking the required ports.
    \item Ensure the correct IP address and port are specified in the configuration files.
    \item Use network diagnostic tools like \texttt{ping} and \texttt{traceroute} to identify connectivity issues.
\end{enumerate}

\section{Troubleshooting Steps}
\subsection{Step 1: Identify the Issue}
\begin{enumerate}
    \item Review the error messages and logs to identify the root cause of the issue.
    \item Check the system resources (CPU, memory, disk space) to ensure they are not exhausted.
    \item Verify that all required services are running.
\end{enumerate}

\subsection{Step 2: Apply Solutions}
\begin{enumerate}
    \item Follow the solutions provided in the common issues section.
    \item If the issue persists, search for similar issues in the project's issue tracker or forums.
    \item Consult the project's documentation for additional troubleshooting steps.
\end{enumerate}

\subsection{Step 3: Seek Help}
\begin{enumerate}
    \item If you are unable to resolve the issue, seek help from the project's community or support channels.
    \item Provide detailed information about the issue, including error messages, logs, and steps to reproduce the problem.
\end{enumerate}

\end{document}
